HUME: Human UCCA-Based Evaluation of Machine Translation

### 2016-03-18 paper/main.tex
aaa

\documentclass[11pt]{article}
\usepackage{acl2016}
\usepackage[round]{natbib}
\usepackage{amsmath}
\usepackage{paralist}
\usepackage{subfig}
\usepackage{times}
\usepackage{latexsym}
\usepackage{graphicx}
\usepackage{url}
\usepackage{pgfplotstable}
%\usepackage{hyperref}
\usepackage{color}
\usepackage{lipsum,adjustbox}
\listfiles

@@

\figref{fig:interface} shows the HUME annotation interface.
% We now describe the HUME annotation interface, shown in \figref{fig:interface}. 
% %We turn to discuss the interface for collecting human judgements on the semantic units
% %of the source, relating to the translation. 
% UCCA annotations of the source are done offline,
% using the UCCA web application.
% %\figref{fig:interface} presents the user interface of HUME. 
% The translation appears at the top, and
% the source sentence directly below it. Underneath the source sentence appears
% its list of semantic units. 
% %For each semantic unit, including the one for the
% %entire source sentence, there is a textbox, displaying the yield of that unit.
% %Information on the category of the unit (e.g., whether it is a Scene, participant etc.).
The user is asked to select a label for each source semantic unit,
by clicking the ``A'', ``B'', Green, Orange, or Red buttons to the right of the unit's box.
%Note that the UCCA labels are not shown.

@@

\tabref{tab:annot}
shows the total number of sentences and nodes annotated by each annotator. Note
that not all nodes in all sentences were annotated. Sometimes,
%this was because
the annotator did not finish a sentence or accidentally missed a node, but in many cases it was also because it was an implicit 
UCCA node, which was not shown to the annotators since there is no corresponding source segment.
\begin{table}
\begin{center}
{\small
\begin{tabular}{ll|cccc}
& & cs & de & pl & ro \\
\hline
Sentences &  Annot. 1 & 324   & 339  & 351  & 230  \\
 & Annot. 2 & 205 & 104  & 340  & 337 \\
\hline
Nodes & Annot. 1 & 8794  & 9253 & 9557  & 6152 \\
 &Annot. 2 & 5553 & 2906  & 9303  & 9228  \\
\end{tabular}
\caption{Total numbers of sentences and nodes annotated on the MT output.}
\label{tab:annot}
}
\end{center}
\end{table}

>>>>

\documentclass[11pt]{article}
\usepackage{acl2016}
\usepackage[round]{natbib}
\usepackage{amsmath}
\usepackage{paralist}
\usepackage{subfig}
\usepackage{times}
\usepackage{latexsym}
\usepackage{graphicx}
\usepackage{url}
\usepackage{pgfplotstable}
%\usepackage{hyperref}
\usepackage{color}
\usepackage{lipsum,adjustbox}

\makeatletter
\renewcommand{\paragraph}{
  \@startsection{paragraph}{4}
  {\z@}{.3ex \@plus .3ex \@minus .2ex}{-1em}
  {\normalfont\normalsize\bfseries}
}
\makeatother

@@

\figref{fig:interface} shows the HUME annotation interface.
% We now describe the HUME annotation interface, shown in \figref{fig:interface}. 
% %We turn to discuss the interface for collecting human judgements on the semantic units
% %of the source, relating to the translation. 
% UCCA annotations of the source are done offline,
% using the UCCA web application.
% %\figref{fig:interface} presents the user interface of HUME. 
% The translation appears at the top, and
% the source sentence directly below it. Underneath the source sentence appears
% its list of semantic units. 
% %For each semantic unit, including the one for the
% %entire source sentence, there is a textbox, displaying the yield of that unit.
% %Information on the category of the unit (e.g., whether it is a Scene, participant etc.).
The user is asked to select a label for each source semantic unit,
by clicking the ``A'', ``B'', Green, Orange, or Red buttons to the right of the unit's box.
Units with multiple parents (as with ``Tom'' in \figref{fig:hume_tree_v2}) are displayed
twice, once under each of their parents, but are only annotatable in one of
their instances, to avoid double counting.
%Note that the UCCA labels are not shown.

@@

\tabref{tab:annot}
shows the total number of sentences and nodes annotated by each annotator. Note
that not all nodes in all sentences were annotated, often
due to
%this was because
the annotator not finishing a sentence or accidentally missing a node.
%, but in many cases it was also because it was an implicit 
%UCCA node, which was not shown to the annotators since there is no corresponding source segment.
\begin{table}
\begin{center}
{\small
\begin{tabular}{ll|cccc}
& & cs & de & pl & ro \\
\hline
Sentences &  Annot. 1 & 324   & 339  & 351  & 230  \\
 & Annot. 2 & 205 & 104  & 340  & 337 \\
\hline
Nodes & Annot. 1 & 8794  & 9253 & 9557  & 6152 \\
 &Annot. 2 & 5553 & 2906  & 9303  & 9228  \\
\end{tabular}
\caption{Total numbers of sentences and nodes annotated on the MT output.}
\label{tab:annot}
}
\end{center}
\end{table}
